Study of the numerical solution of X-Modes equations around the hybrid resonnance

### 2015-01-27 report/intro.tex
added really bad sentence to emphasize more than the "additionnaly"
revised LM

We consider the model of cold plasma of \cite{Stix} which is described by the non-stationary Maxwell system  
\begin{align}
-\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
\mu_0 \partial_t \Hbf + \curl\, \E = 0
\end{align}
coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, and takes into account the friction  $\nu$ between particles
\be
m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
\ee
The unknows are the electromagnetic field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, 
the electronic current $\J$, 
and the velocity of electrons $\ubf_e$. Here $B_0$ is the background magnetic field, typically assumed to be uniform in time and space.  
We denote by $e<0$ the value of the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
depends on spatial variables and is uniform in time. 
Without loss of generality, we set $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, which allows to obtain the following system of equations 
\begin{align}
\label{eq:main_model}
\begin{split}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{split}
\end{align}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
The energy of this system for $\nu=0$ in a domain $\Omega$ can be expressed as \cite{stable_yee_plasma_current}
\begin{align*}
{\mathcal E}(t)= \int_\Omega \left(
\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} \mathrm{d}\x.
\right)
\end{align*}
From this it can be seen that if the electron density $N_e(x)$ vanishes, 
the energy blows up~\cite{stable_yee_plasma_current}. 
Mathematically, this effect was recently investigated in \cite{Despres_2014}, 
in particular, it was shown that the electric field $E_x$ in this case is no longer square 
integrable, and explicit estimates on the behaviour of the solutions of \eqref{eq:main_model} in 1D were given.

In this work we look at a simplification of this model obtained after 
the Fourier transform of (\ref{eq:main_model}) in $y$.

The goal of this article is two-fold. 
First, we investigate the finite element approximation of the 1D 
problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$).
\mrev{More precisely, 
\begin{align*}
%\label{eq:main_frequency_domain_1}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-
\epsilon(\omega)\hat{\mathbf{E}}=0,\\
\epsilon(\omega)=\left(
\begin{matrix}
 \tilde{\alpha} & i\tilde{\delta} \\
 -i\tilde{\delta}  & \tilde{\alpha}
\end{matrix}
\right),\\
\tilde{\alpha}(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\tilde{\omega}\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)}\right),\qquad 
\tilde{\delta}(\omega)=\frac{\omega_c\omega_p^2}{\omega(\tilde{\omega}^2-\omega_c^2)},\\
\tilde{\omega}=\omega+i\nu,\qquad \omega_c=\mrev{\frac{eB_0}{m_e}},\qquad \omega_p^2=\frac{e^2 N_e}{\epsilon_0 m_e}.
\end{align*}
After expansion in $\nu\rightarrow 0$ and keeping lower-order terms only
\begin{align*}
 \tilde{\alpha}(\omega)=\alpha(\omega)+i\nu\frac{\omega_p^2(\omega^2+\omega_c^2)}{(\omega^2-\omega_c^2)^2}\frac{\omega^2}{c^2},\qquad \alpha(\omega)=\frac{\omega^2}{c^2}\left(1-\frac{\omega_p^2}{\omega^2-\omega_c^2}\right),\\
 \tilde{\delta}(\omega)=\delta(\omega)-\frac{2i\omega^3\nu}{c^2(\omega^2-\omega_c^2)^2},\qquad \delta(\omega)=\frac{\omega\omega_c\omega_p^2}{c^2(\omega^2-\omega_c^2)}.
\end{align*}
Then the limiting absorption principle can be obtained leaving only the diagonal terms in the above expansion (see \cite{Despres_2014}):
\begin{align}
\label{eq:main_frequency_domain}
\operatorname{curl}\operatorname{curl}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}
\left(\epsilon_0(\omega)+\nu Id\right)\hat{\mathbf{E}}=0,\\
\nonumber
\epsilon_0(\omega)=\left(
\begin{matrix}
 \alpha & i\delta \\
 -i\delta & \alpha 
\end{matrix}
\right)
\end{align}
}
\urev{Additionally, we assume $\alpha(\omega)$ and $\delta(\omega)$ be sufficiently smooth, i.e. bounded and continuous in  
$\left[-L,\; \mathbb{R}\right)$.}
In particular, we again investigate this problem in one dimension, performing the Fourier transform in $y$.
We prove the well-posedness of this problem for $\nu>0$ in Section~\ref{sec:wellposedness} and 
demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity 
of the solution fairly well (Section \ref{sec:freq_dep}). 
Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.

To our knowledge, such numerical studies have not been performed in the existing literature.

To solve the problem (\ref{eq:main_model}) numerically, we equip it with the following boundary conditions.
At the left boundary of the domain we choose Robin boundary conditions 
\be
-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$. We truncate the domain 
$(-L,\; \mathbb{R})$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
\begin{remark}
	When modelling antennas in plasma physics, in such applications as ITER, 
	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
\end{remark}

>>>>

We consider the model of cold plasma of \cite{Stix} which is described by the 2D time-dependent Maxwell system  
\begin{align}
-\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
\mu_0 \partial_t \Hbf + \curl\, \E = 0
\end{align}
coupled with a linear electronic current  $\J = eN_e \ubf_e$, 
\be
m_e \partial_t \ubf_e =e (\E +\ubf_e \wedge B_0) -m_e \nu \ubf_e, \label{eq:electronmove}
\ee
where $\nu$ is  the friction  between particles.
The unknowns are the electromagnetic fields $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, 
 %the electronic current $\J$, 
and the velocity of electrons $\ubf_e$. Here $B_0$ is the background magnetic field, typically assumed to be uniform in time and space.  
We denote by $e<0$ the value of the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
depends on spatial variables and is uniform in time. 
Without loss of generality, we set $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, which allows to obtain the following system of equations 
\begin{align}
\label{eq:main_model}
\left\{\begin{array}{l}
\epsilon_0\partial_t E_{x}-\partial_y H_z=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
\mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{array}
\right.\end{align}
posed in $[-L,\; \infty)\times \mathbb{R}$, for some $L>0$. This domain represents the physical case of a wave sent from a wall facing a plasma. 
The energy of this system for $\nu=0$ in a domain $\Omega\in\mathbb R^2$ can be expressed as \cite{stable_yee_plasma_current}
\begin{align*}
{\mathcal E}(t)= \int_\Omega \left(
\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} 
\right)\mathrm{d}\x.
\end{align*}
So if the electron density $N_e(x)$ vanishes, 
the energy blows up~\cite{stable_yee_plasma_current}. 
Mathematically, this effect was recently investigated in \cite{Despres_2014}, 
in particular, it was shown that the electric field component $E_x$ in this case is no longer square 
integrable, and explicit estimates on the behaviour of the solutions of \eqref{eq:main_model} in 1D were provided.

We complement Problem (\ref{eq:main_model}) with the following boundary conditions.
At the left boundary of the domain, which represents the wall, we choose Robin boundary conditions 
\be
-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath\lambda\E_{inc} \wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$. We truncate the domain 
$(-L,\; \infty)$ to $(-L,\; H)$ and set on the right boundary $\operatorname{curl} \E = 0$. 
\begin{remark}
	When modeling antennas in plasma physics, in such applications as ITER, 
	a good choice of boundary condition could be $\lambda = \sqrt{\alpha(-L)}$
\end{remark}

The goal of this article is two-fold. 
First, we investigate the finite element approximation of the 1D 
problem \eqref{eq:main_model} written in the frequency domain ($\partial_t\rightarrow -i\omega$), with a linearized dielectric tensor with respect to $\nu$.
In particular, we again investigate this problem in one dimension, performing the Fourier transform in $y$.
We prove the well-posedness of this problem for $\nu>0$ in Section~\ref{sec:wellposedness} and 
demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity 
of the solution fairly well (Section \ref{sec:freq_dep}). 
Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$. DRAWING A COMMUTATIVE DIAGRAM ?
To our knowledge, such numerical studies have not been performed in the existing literature.

### 2015-01-27 report/timedomain.tex
experiments adding+ formatting has changed a bit
full working version of the documents
add refs to yee plasma current paper on timedomain.tex
revised LM

The equations of consideration for the one dimensionnal model write as
 \begin{align}
 \epsilon_0\partial_t E_{x}=-eN_e u_x, \nonumber\\
 \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
 \mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0, \label{eq:tdpb}\\
 m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
 m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
 \end{align}
We compute a numerical approximation of~\eqref{eq:tdpb} on a Cartesian grid using the Yee scheme. Let $n$ denote the time step, as usual $t_n = n \Delta t$. $H_z$ will then be taken on a half time step, and our equation, discretized in them write :
 \begin{align}
 \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e u_x, \nonumber\\
 \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z=-eN_e u_y,\nonumber\\
 \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y-\partial_y E_x=0, \label{eq:tdiscretizedpb}\\
 m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
 m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
 \end{align}
 We discretize our equation on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid. Evidently we already stated it for $H_z$ in the time discretization. Fig.~\ref{schemepos} shows the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time. We obtain the following discretized equations,

\be 
\eps_0 \frac{E_x\inp- E_x\midin}{\Delta t} = -e N_e \frac{u_x\inp + u_x \midin}{2},
\label{eq:ns1}
\ee 
\be
\eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -eN_x \frac{u_y\ihnp + u_y\ihn}{2} ,
\label{eq:ns2}
\ee
\be
 \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0,
 \label{eq:ns3}
\ee
\be 
m_e \frac{u_x\inp-u_x\midin }{\Delta x} = e N_e \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2},
\label{eq:ns4}
\ee
\be
m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2},
\ee
\input{grid}

We first compute $H_z$ at time $n+1/2$ with \eqref{eq:ns3}. Then, \eqref{eq:ns2} gives the expression $E_y\ihnp$ as a function of known variables, and $u_y^{n+1}$, as follow
\be
E_y\ihnp = E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}.
\label{eq:ns5}
\ee

By incorporating this expression into \eqref{eq:ns5} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
\be 
\begin{array}{l}
u_y\ihnp m_e = m_e u_y\ihn + \Delta t eN_e \frac{E_y\ihn}{2}\\
+ \Delta teN_e\left(E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}\right) \\
-\nu \Delta t m_e \frac{u_y\ihnp +u_y\ihn}{2}-\Delta teB_0 \frac{u_x\midin-u_x\inp}{2},
\end{array}
\label{eq:ns6}
\ee
which gives the following expression for $u_y\ihnp$

\begin{align}
u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right) =&\left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn +\Delta t eN_e E_y\ihn \nonumber\\
&- \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x} - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right),
\label{eq:ns7} 
\end{align}
which we write 
\begin{align}
u_y\ihnp K_1&= K_2 u_y\ihn +\Delta t eN_e E_y\ihn-  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
\label{eq:ns7bis} 
\end{align}
with $K_1 =  m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$ and $K_2 =m_e(1- \frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$.

Now we just need an expression of $E_x\inp$ as a function of time $n$ variables and $u_x^{n+1}$ and putting \eqref{eq:ns7} in \eqref{eq:ns4}, the scheme will be explicit. 
We can find such and expression in \eqref{eq:ns1}
\be 
E_x\inp = E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}.
\label{eq:ns8}
\ee

We then have the scheme

\begin{align}
m_e u_x\inp= & m_e u_x\midin  + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right) + \Delta t  e N_e \frac{1}{2}E_x\midin -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\nonumber\\
&+  \frac{e B_O \Delta t}{2K_1}\Big(K_2 u_y\ihn +\Delta t eN_e E_y\ihn -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\nonumber\\
&- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right)\Big)+  \frac{1}{2}\Delta teB_0u_y\ihn,
\label{eq:ns9}
\end{align}

which one can simplify into
\begin{align}
u_x & \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp 
= \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin \nonumber\\
& + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
&\label{eq:ns10} 
\end{align}
and the scheme is then fully explicit.

>>>>

\section{Time Dependent Problem Discretization}
EXPLAIN HOW IS THIS SYSTEM OBTAINED FROM THE SYSTEM PROVIDED IN THE INTRO

 \begin{align}
 \epsilon_0\partial_t E_{x}=-eN_e u_x, \nonumber\\
 \epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\nonumber\\
 \mu_0\partial_t H_z+\partial_x E_y-\partial_y E_x=0, \label{eq:tdpb}\\
 m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
 m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
 \end{align}
We compute a numerical approximation of~\eqref{eq:tdpb} on a Cartesian grid using the Yee scheme, as  suggested in \cite{stable_yee_plasma_current}. Let $n$ denote the time step index, as usual $t_n = n \Delta t$. The unknown $H_z$ will then be discretized on half time steps, $t_{n+1/2}$. The time discretization of the system reads:
 \begin{align}
 \left\{\begin{array}{l}
 \epsilon_0\frac{ E_{x}^{n+1}-E_x^{n}}{\Delta t}=-eN_e u_x, \nonumber\\
 \epsilon_0\frac{ E_{y}^{n+1}-E_y^{n}}{\Delta t}+\partial_x H_z=-eN_e u_y,\nonumber\\
 \mu_0\frac{ H_z^{n+1/2}-H_z^{n-1/2}}{\Delta t}+\partial_x E_y-\partial_y E_x=0, \label{eq:tdiscretizedpb}\\
 m_e\frac{ u_{x}^{n+1}-u_x^{n}}{\Delta t}=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
 m_e\frac{u_{y}^{n+1}-u_y^{n}}{\Delta t}=eE_y-eu_xB_0-\nu m_e u_y.\nonumber
\end{array}\right.
 \end{align}
The space discretization is performed on staggered grid, meaning $E_x$, $u_x$, $E_y$, $u_y$ and $H_z$ are not and the same grid points. RAPID JUSTIFICATION ?  Fig.~\ref{schemepos} shows the positions of $Ex$, $u_x$ (black dots), $E_y$ $u_y$ (blue dots) and $H_z$ (red dots) on the discretized grid in space and time. The fully discretized system then reads

\be 
\eps_0 \frac{E_x\inp- E_x\midin}{\Delta t} = -e N_e \frac{u_x\inp + u_x \midin}{2},
\label{eq:ns1}
\ee 
\be
\eps_0 \frac{E_y\ihnp-E_y\ihn}{\Delta t}+ \frac{H_z\ipnh-H_z\inh}{\Delta x} = -eN_x \frac{u_y\ihnp + u_y\ihn}{2} ,
\label{eq:ns2}
\ee
\be
 \frac{H_z\inh-H_z\inmh}{\Delta t}+ \frac{E_y\ihn-E_y\imhn}{\Delta x}=0,
 \label{eq:ns3}
\ee
\be 
m_e \frac{u_x\inp-u_x\midin }{\Delta x} = e N_e \frac{E_x\inp+E_x\midin}{2}-\nu m_e\frac{u_x\inp+u_x \midin}{2}+ eB_0\frac{u_y\ihn+u_y\ihnp}{2},
\label{eq:ns4}
\ee
\be
m_e \frac{u_y\ihnp-u_y\ihn}{\Delta t} = eN_e \frac{E_y\ihnp + E_y\ihn}{2}- \nu m_e \frac{u_y\ihnp +u_y\ihn}{2}-eB_0 \frac{u_x\midin+u_x\inp}{2},
\label{eq:ns401}
\ee
\input{grid}

It is now possible to describe explicitly how to solve the proviso discrete system. We first compute $H_z$ at time $n+1/2$ with \eqref{eq:ns3}. Then, \eqref{eq:ns2} gives the expression $E_y\ihnp$ as a function of known variables, and $u_y^{n+1}$, as follow
\be
E_y\ihnp = E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}.
\label{eq:ns5}
\ee

By incorporating this expression into \eqref{eq:ns401} we then obtain $u_y$ at time $n+1$ as a function of known variables and $u_x^{n+1}$, 
\be 
\begin{array}{l}
u_y\ihnp m_e = m_e u_y\ihn + \Delta t eN_e \frac{E_y\ihn}{2}\\
+ \Delta teN_e\left(E_y\ihn - \frac{\Delta t }{\eps_0}\frac{H_z\ipnh-H_z\inh}{\Delta x} - \frac{\Delta t e N_e}{\eps_0}\frac{u_y\ihnp + u_y\ihn}{2}\right) \\
-\nu \Delta t m_e \frac{u_y\ihnp +u_y\ihn}{2}-\Delta teB_0 \frac{u_x\midin-u_x\inp}{2},
\end{array}
\label{eq:ns6}
\ee
or equivalently the explicit expression
\begin{align}
u_y\ihnp \left(m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right) =&\left(m_e(1-\frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}\right)u_y\ihn +\Delta t eN_e E_y\ihn \nonumber\\
&- \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x} - \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
\label{eq:ns7} 
\end{align}
To simplify this expression, consider
\begin{align}
u_y\ihnp K_1&= K_2 u_y\ihn +\Delta t eN_e E_y\ihn-  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}- \frac{e Bo \Delta t}{2}\left(u_x\midin+u_x\inp\right).
\label{eq:ns7bis} 
\end{align}
with $K_1 =  m_e(1+\frac{\Delta t \nu}{2}) +\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$ and $K_2 =m_e(1- \frac{\Delta t \nu}{2}) -\frac{\left(\Delta t e N_e\right)^ 2}{2\eps_0}$.

At this point only $E_x^{n+1}$ and $u_x^{n+1}$ still need to be computed. 
Since \eqref{eq:ns1} reads
\be 
E_x\inp = E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2},
\label{eq:ns8}
\ee
we then have the scheme 
\begin{align}
m_e u_x\inp= & m_e u_x\midin  + \Delta t e N_e \frac{1}{2}\left( E_x\midin - \frac{\Delta t e N_e}{\eps_0}\frac{u_x\inp + u_x\midin}{2}\right) + \Delta t  e N_e \frac{1}{2}E_x\midin -\Delta t\nu m_e\frac{u_x\inp+u_x \midin}{2}\nonumber\\
&+  \frac{e B_0 \Delta t}{2K_1}\Big(K_2 u_y\ihn +\Delta t eN_e E_y\ihn -  \frac{(\Delta t )^2 e N_e}{2\eps_0} \frac{H_z \ipnh- H_z \inh}{\Delta x}\nonumber\\
&- \frac{e B_0 \Delta t}{2}\left(u_x\midin+u_x\inp\right)\Big)+  \frac{1}{2}\Delta teB_0u_y\ihn,
\label{eq:ns9}
\end{align}
which can be simplified as
\begin{align}
 \left(me(1+\frac{\Delta t \nu}{2})+ \frac{(eB_0\Delta t)^2}{4K_1} + \frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\inp 
= \left(me(1-\frac{\Delta t \nu}{2})- \frac{(eB_0\Delta t)^2}{4K_1} -\frac{(e\Delta t N_e)^2}{4\eps_0}\right) u_x\midin \nonumber\\
 + e \Delta t N_e E_x \midin  + \left( \frac{eB_0 \Delta t K_2}{2 K_1}+ \frac{e B_0 \Delta t}{2}\right) u_y\ihn - \frac{(e\Delta t)^2 N_e B_0}{2K_1}E_y\ihn  - \frac{e^2(\Delta t)^3 B_0}{4K_1}\frac{H_z \ipnh- H_z \inh}{\Delta x},
\label{eq:ns10} 
\end{align}
and the scheme is then fully explicit.

To summarize, the algorithm to solve the discrete system \eqref{} is
\begin{itemize}
\item compute $H_z^{n+1/2}$ thanks to \eqref{eq:ns3},
\item compute $E_y^{n+1/2}$ thanks to \eqref{eq:ns6},
\item compute $u_y^{n+1}$ thanks to \eqref{eq:ns7bis},
\item compute $u_x^{n+1}$ thanks to \eqref{eq:ns10},
\item compute $E_x^{n+1}$ thanks to \eqref{eq:ns8}.
\end{itemize}
